Non-Vertical Cultural Transmission and the\\ Evolution of Cooperation

### 2020-09-01 ms/main.tex
another fix to result 3

% in beta
%\begin{enumerate}
%\item \emph{Fixation of cooperation}: 
%	if \emph{(i)} $T=T_A=T_B$ and $c < b\cdot \frac{\alpha T}{1-T}$; or
%	if \emph{(ii)} $T_A>T_B$ and $0<\beta_3$; or 
%	if \emph{(iii)} $T_A<T_B$ and $\beta_1<\beta_3$.
%\item \emph{Fixation of the defection}: 
%	if \emph{(iv)}  $T=T_A=T_B$ and $c > b\cdot \frac{\alpha T}{1-T}$; or 
%	if \emph{(v)} $T_A>T_B$ and $\beta_1<\beta_3<0$; or 
%	if \emph{(vi)} $T_A<T_B$ and $\beta_3<0$.
%\item \emph{Coexistence of both phenotypes at $\hat{p}^*$}: 
%	if \emph{(vii)} $T_A < T_B$ and $0<\beta_3<\beta_1$.
%\item \emph{Fixation of either phenotype depending on initial frequency}:
%	if \emph{(viii)}  $T_A>T_B$ and $\beta_3<\beta_1$.
%\end{enumerate}

% in gamma
\begin{enumerate}
\item \emph{Fixation of cooperation}: 
	if \emph{(i)} $T=T_A=T_B$ and $c < b\cdot \frac{\alpha T}{1-T}$; or
	if \emph{(ii)} $T_A>T_B$ and $c < \hat\gamma_1$; or 
	if \emph{(iiia)} $T_A<T_B$ and $v>\hat v$ and $c < \hat\gamma_2$; or
	if \emph{(iiib)} $T_A<T_B$ and $v<\hat v$ and $c > \hat\gamma_2$.
\item \emph{Fixation of the defection}: 
	if \emph{(iv)}  $T=T_A=T_B$ and $c > b\cdot \frac{\alpha T}{1-T}$; or 
  if \emph{(v)} $T_A>T_B$ and $\hat{\gamma_1} < c < \hat{\gamma_2}$; or 
	if \emph{(vi)} $T_A<T_B$ and $c>\hat{\gamma_1}$.
\item \emph{Coexistence of both phenotypes at $\hat{p}^*$}: 
  if \emph{(viia)} $T_A < T_B$ and $v<\hat{v}$ and $\hat{\gamma_1}<c<\hat{\gamma_2}$; or
  if \emph{(viib)} $T_A < T_B$ and $v>\hat{v}$ and $c>\hat{\gamma_1}$ and $c>\hat{\gamma_2}$. %$0<\beta_3<\beta_1$.
\item \emph{Fixation of either phenotype depending on initial frequency}:
  if \emph{(viii)}  $T_A>T_B$ and $c > \hat{\gamma_2}$ and $v>\hat{v}$.
\end{enumerate}
\end{result}

>>>>

% in beta
%\begin{enumerate}
%\item \emph{Fixation of cooperation}: 
%	if \emph{(i)} $T=T_A=T_B$ and $c < b\cdot \frac{\alpha T}{1-T}$; or
%	if \emph{(ii)} $T_A>T_B$ and $0<\beta_3$; or 
%	if \emph{(iii)} $T_A<T_B$ and $\beta_1<\beta_3$.
%\item \emph{Fixation of the defection}: 
%	if \emph{(iv)}  $T=T_A=T_B$ and $c > b\cdot \frac{\alpha T}{1-T}$; or 
%	if \emph{(v)} $T_A>T_B$ and $\beta_1<\beta_3<0$; or 
%	if \emph{(vi)} $T_A<T_B$ and $\beta_3<0$.
%\item \emph{Coexistence of both phenotypes at $\hat{p}^*$}: 
%	if \emph{(vii)} $T_A < T_B$ and $0<\beta_3<\beta_1$.
%\item \emph{Fixation of either phenotype depending on initial frequency}:
%	if \emph{(viii)}  $T_A>T_B$ and $\beta_3<\beta_1<0$.
%\end{enumerate}

% in gamma
\begin{enumerate}
\item \emph{Fixation of cooperation}: 
	if \emph{(i)} $T=T_A=T_B$ and $c < b\cdot \frac{\alpha T}{1-T}$; or
	if \emph{(ii)} $T_A>T_B$ and $c < \hat\gamma_1$; or 
	if \emph{(iiia)} $T_A<T_B$ and $v>\hat v$ and $c < \hat\gamma_2$; or
	if \emph{(iiib)} $T_A<T_B$ and $v<\hat v$ and $c > \hat\gamma_2$.
\item \emph{Fixation of the defection}: 
	if \emph{(iv)}  $T=T_A=T_B$ and $c > b\cdot \frac{\alpha T}{1-T}$; or 
  if \emph{(v)} $T_A>T_B$ and $\hat{\gamma_1} < c < \hat{\gamma_2}$; or 
	if \emph{(vi)} $T_A<T_B$ and $c>\hat{\gamma_1}$.
\item \emph{Coexistence of both phenotypes at $\hat{p}^*$}: 
  if \emph{(viia)} $T_A < T_B$ and $v<\hat{v}$ and $c<\hat{\gamma_1}$ and $c<\hat{\gamma_2}$; or
  if \emph{(viib)} $T_A < T_B$ and $v>\hat{v}$ and $c<\hat{\gamma_1}$ and $c>\hat{\gamma_2}$. %$0<\beta_3<\beta_1$.
\item \emph{Fixation of either phenotype depending on initial frequency}:
  if \emph{(viii)}  $T_A>T_B$ and $c > \hat{\gamma_2}$ and $c > \hat{\gamma_1}$ and $v>\hat{v}$.
\end{enumerate}
\end{result}
